\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}


\usepackage{times}
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{inconsolata}
\usepackage{graphicx}

\usepackage{enumitem}
\setlist[itemize]{noitemsep, nosep}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{To intervene or not to intervene}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
	%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
	%         \And  ... \And
	%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
	%         \AND
	%         Author 2 \\ Address line \\ ... \\ Address line \And
	%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
	Affiliation / Address line 1 \\
	Affiliation / Address line 2 \\
	Affiliation / Address line 3 \\
	\texttt{email@domain} \\\And
	Second Author \\
	Affiliation / Address line 1 \\
	Affiliation / Address line 2 \\
	Affiliation / Address line 3 \\
	\texttt{email@domain} \\}

%\author{
	%  \textbf{First Author\textsuperscript{1}},
	%  \textbf{Second Author\textsuperscript{1,2}},
	%  \textbf{Third T. Author\textsuperscript{1}},
	%  \textbf{Fourth Author\textsuperscript{1}},
	%\\
	%  \textbf{Fifth Author\textsuperscript{1,2}},
	%  \textbf{Sixth Author\textsuperscript{1}},
	%  \textbf{Seventh Author\textsuperscript{1}},
	%  \textbf{Eighth Author \textsuperscript{1,2,3,4}},
	%\\
	%  \textbf{Ninth Author\textsuperscript{1}},
	%  \textbf{Tenth Author\textsuperscript{1}},
	%  \textbf{Eleventh E. Author\textsuperscript{1,2,3,4,5}},
	%  \textbf{Twelfth Author\textsuperscript{1}},
	%\\
	%  \textbf{Thirteenth Author\textsuperscript{3}},
	%  \textbf{Fourteenth F. Author\textsuperscript{2,4}},
	%  \textbf{Fifteenth Author\textsuperscript{1}},
	%  \textbf{Sixteenth Author\textsuperscript{1}},
	%\\
	%  \textbf{Seventeenth S. Author\textsuperscript{4,5}},
	%  \textbf{Eighteenth Author\textsuperscript{3,4}},
	%  \textbf{Nineteenth N. Author\textsuperscript{2,5}},
	%  \textbf{Twentieth Author\textsuperscript{1}}
	%\\
	%\\
	%  \textsuperscript{1}Affiliation 1,
	%  \textsuperscript{2}Affiliation 2,
	%  \textsuperscript{3}Affiliation 3,
	%  \textsuperscript{4}Affiliation 4,
	%  \textsuperscript{5}Affiliation 5
	%\\
	%  \small{
		%    \textbf{Correspondence:} \href{mailto:email@domain}{email@domain}
		%  }
	%}

\begin{document}
	\maketitle
	\begin{abstract}
		This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences.
		The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
		These instructions should be used both for papers submitted for review and for final versions of accepted papers.
	\end{abstract}
	
	
	\section{Introduction}
	\textbf{Dimitris, Katerina}
	
	
	\section{Related Work}
	
	\subsection{Human facilitators}
	\textbf{Katerina, Dimitris} Add research on how humans typically behave when facilitating.
	
	\subsection{Facilitation detection}
	\textbf{Dimitris} Add work that already tried to answer this question (Fora, WHoW, the second whow aussie paper).
	
	
	\section{Dataset}


	\begin{table*}[ht]
		\centering
		\begin{tabular}{|l|c|l|l|}
			\hline
			\textbf{Name} & \textbf{\#comments} & \textbf{Domain} & \textbf{Format} \\ \hline
			WikiDisputes \citeyearpar{wikidisputes} & 96,320 & Forum & Text \\ \hline
			WikiTactics \citeyearpar{wikitactics} & 3,850 & Forum & Text \\ \hline
			WikiConv \citeyearpar{wikiconv} & 17,806,373 & Forum & Text \\ \hline
			Conversations Gone Awry / CMV II \citeyearpar{cmv_awry2}& 40,607 & Forum & Text \\ \hline
			CeRI \citeyearpar{ceri} & 3,700 & Forum & Text \\ \hline
			User Moderation (UMOD) \citeyearpar{umod}& 2,000 & Forum & Text \\ \hline
			Intelligence Squared 2 (IQ2) \citeyearpar{zhang-etal-2016-conversational}& 34,245 & Debate & Oral \\ \hline
			Why How Who (WHoW) \citeyearpar{chen-etal-2025-whow} & 25,542 & Radio / TV & Oral \\ \hline
			Fora \citeyearpar{schroeder-etal-2024-fora} & 39,438 & Deliberation & Oral \\ \hline
		\end{tabular}
		\caption{The datasets used in PEFK. We include a large variety of domains, and two different sources; text-only datasets, and transcripts from oral discussions.}
		\label{tab:datasets}
	\end{table*}


	\subsection{Description}
	\citet{korre-etal-2025-evaluation} provide a list of datasets relating to discussion facilitation. We combine all of these datasets, preprocess them (\ref{app:dataset:preprocessing}) and standardize their data according to a simple, unified schema (\ref{app:dataset:schema}). We thus create a multi-domain dataset focused around facilitation, called the Prosocial and Effective Facilitation in Konversations (PEFK). Unlike its predecessors, PEFK is both rich in size and comment-level information, allowing us to run thorough analysis between similar datasets.
	
	
	\subsection{Text-based vs. transcribed datasets}
	\textbf{Dimitris, Katerina} Our datasets are fundamentally different depending on whether the data are transcripts or actual text data. Dimitris will add technical examples (i.e., how the transcriptions have a different format, e.g., comments that cut each other off). Katerina will add social science research on how oral and written speech differs. Thus, we run separate experiments for each of the two dataset types.
	
	
	\section{How to decide when to intervene?}
	
	\subsection{Do not decide}
	\textbf{Dimitris}. What most platforms do is to use flagging and reports to decide when to intervene. Mention Grok as a facilitative agent that works by invocation only. Briefly talk about advantages and disadvantages of current approach.
	
	
	\subsection{Use humans}
	
	\subsubsection{Merits and disadvantages}
	\textbf{Katerina}. Humans may be the ``best'' classifier since they understand context and social behavior best, but they are not scalable (cite our survey). 
	Dimitris can add cost calculations for a hypothetical scenario to drive point home.
	
	
	\subsubsection{Experimental setup}
	\textbf{Katerina}. Annotation study. We leave experimental details for the appendix, but mention expert annotators, basic procedure, data and setup here. Also talk about positive vs negative reinforcement.
	
	\subsubsection{Results}
	\textbf{Katerina}. Inter-annotator agreement and discussion.
	
	
	\subsection{Use LLMs}
	
	\subsubsection{Can we detect facilitation interventions?}
	\textbf{Dimitris}. We use LLMs and transformer-based models to decide whether the person talking is a facilitator.
	
	
	\subsubsection{Can LLMs decide when to intervene?}
	\textbf{Dimitris, Katerina}. No. We show this with two experiments. One is agreement between humans and LLMs on the annotation task (strong baseline). The other is by predicting when a facilitator would speak (weak baseline).
	
	
	\section{Conclusion}
	Humans are good but expensive. Our research is good. We wasted a good amount of money on this, please accept this.

	
	

	\bibliography{refs}
	\clearpage
	\appendix
	
	\section{Dataset details}
	
	\subsection{Preprocessing}
	\label{app:dataset:preprocessing}
	
	\paragraph{General}
	\begin{itemize}
		\item We exclude comments with no text.
		\item We exclude discussions with less than two distinct participants.
		\item We exclude discussions which are common between wikitactics and wikiconv as well as wikidisputes and wikiconv.
		\begin{itemize}
			\item There may be duplicate discussions between wikidisputes and wikitactics, but we allow them since they feature complementary information.
		\end{itemize}
	\end{itemize}
	
	\paragraph{Wikiconv}
	\begin{itemize}
		\item The Wikiconv corpus does not contain information about which user is a moderator/facilitator. Therefore, all comments relating to Wikiconv are tagged as non-moderators.
		\item Additionally, we follow the instructions of the original researchers \cite{wikiconv}, and select only discussions which have at least two comments by different users.
		\begin{itemize}
			\item Wikipedia (thankfully) does not track users who log in with only an IP address (in the original dataset, their \texttt{user\_id} is always set to 0 and their username is of the form \texttt{211.111.111.xxx}. We consider each such username to be a separate user.
			\item Due to the size of the dataset, we have to partially load it during preprocessing. Thus, there is a small chance every 100,000 records that a discussion is marked as a false negative and a part of it gets discarded.
			\item We only include English comments in the final dataset. We use a small, efficient library (\texttt{py3langid}) for language recognition, due to the large size of Wikiconv. Non-English comments are discarded before selecting valid discussions (see point above).
		\end{itemize}
	\end{itemize}
	
	\paragraph{Wikitactics}
	\begin{itemize}
		\item We infer facilitative actions by whether the comment belongs in any of the following categories:
		\begin{itemize}
			\item Asking questions
			\item Coordinating edits
			\item Providing clarification
			\item Suggesting a compromise
			\item Contextualisation
		\end{itemize}
		\item The above tactics are a subset of the Coordinative labels used in the WikiTactics paper. They were selected because they are not used necessarily on 1-1 discussions; they could reasonably be applied by third-party participants. Contrast them with other Coordinative labels such as ``Conceding/recanting'' and ``I don't know''.
	\end{itemize}
	
	\paragraph{Wikidisputes}
	\begin{itemize}
		\item Since only 0.03\% of the comments in the dataset are made by moderators, we mark the dataset as not supporting moderation.
	\end{itemize}
	
	\paragraph{UMOD}
	\begin{itemize}
		\item Facilitative actions are marked as a gradient from 0 (no facilitation) to 1 (full facilitation). We adopt a threshold of 0.75 to consider an action as facilitative, with more than 50\% annotator agreement (measured as entropy in the original dataset).
	\end{itemize}
	
	\paragraph{CMV-AWRY2}
	\begin{itemize}
		\item We mark a discussion as escalated when the derailment value (from the official dataset) is in the 60th upper percentile.
		\item We remove deleted (``[deleted]'') comments.
	\end{itemize}


	\subsection{Dataset Schema}
	\label{app:dataset:schema}
	
	Table~\ref{tab:dataset-columns} details the information available for each comment in the dataset. Some information, such as whether the person talking is a moderator / facilitator, is available only on some sub-datasets. Also note that the \texttt{is\_moderator} column may hold different definitions of what we consider  as moderator / facilitator. UMOD for instance considers facilitative comments made by users, while others such as Fora consider a comment facilitative if it was made by a dedicated facilitator.
	
	\begin{table*}[ht]
		\centering
		\begin{tabular}{|l|l|p{10cm}|}
			\hline
			\textbf{Name} & \textbf{Type} & \textbf{Description} \\ \hline
			conv\_id & string & The discussion's ID. Comments under the same discussion refer to the same discussion ID. \\ \hline
			message\_id & string & The message's (comment's) unique ID. \\ \hline
			reply\_to & string & The ID of the comment which the current comment responds to. nan if the comment does not respond to another comment (e.g., it's the Original Post (OP)). \\ \hline
			user & string & Username or hash of the user that posted the comment \\ \hline
			is\_moderator & bool & Whether the user is a moderator/facilitator. \\ \hline
			moderation\_supported & bool & True if the moderation labels are directly computed from the original dataset \\ \hline
			escalated & bool & A discussion-level measure denoting discussions which have been derailed \\ \hline
			escalation\_supported & bool & True if the escalation labels are directly computed from the original dataset \\ \hline
			text & string & The contents of the comment \\ \hline
			dataset & string & The dataset from which this comment originated from \\ \hline
			notes & JSON & A dictionary holding notable dataset-specific information \\ \hline
			toxicity & float & The ``toxicity'' score given to the comment by the Perspective API \\ \hline
			severe\_toxicity & float & The ``severe toxicity'' score given to the comment by the Perspective API \\ \hline
		\end{tabular}
		\caption{The full set of columns used for each comment in the PEFK dataset.}
		\label{tab:dataset-columns}
	\end{table*}


		
	\end{document}
